%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Blake La Pierre}
\address{(949)~$\cdot$~259~$\cdot$~3040 \\ Nixon, Texas}
\address{blakelapierre@gmail.com \\ github.com/blakelapierre}

\begin{document}

\begin{rSection}{About}
A software developer with direct experience at all levels of the software lifecycle, including requirements gathering, design, analysis, implementation, testing, deployment and maintainence. A rapid learner with the ability to quickly integrate an understanding of a project's goals with the project's details. Has a demonstrated ability to identify and resolve inefficiencies and flawed processes.
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & C\#, Typescript, Javascript, HTML, SQL, Java, CSS/LESS, \\
& C/C++, Python, Ruby, XML \\
Protocols \& APIs & JSON, SOAP, REST \\
Databases & Microsoft SQL Server, PostgreSQL, MySQL, Firebird \\
Frameworks \& Libraries & React, Angular, ExtJS, jQuery, ASP.NET, ASP, Node.js \\
Tools & Git, SVN, TeamCity, Visual Studio, Eclipse, Linux, Windows
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Employment Experience}

\begin{rSubsection}{none}{February 2013 - Present}{Chief Principal Architect}{Connecticut; California; DC; Texas}
\item Vision, research, design, prototyping, implementation, documentation, and marketing.
\item Widespread application of work and educational experience to develop software. Developed proofs-of-concepts \& usable projects, contributed to open source projects, developed open source libraries.
\item Public communication and collaboration on developed software, others' software, science, software, and public interest topics.
\end {rSubsection}

\begin{rSubsection}{Custom Solutions}{December 2015 - April 2016}{Sole Proprietor}{Berkeley, California}
\item Produced custom solutions to client problems.
\item Primary project was a "gamification" for insurance product sales for a client of our client.
\item Interpreted client requirements, architected and delivered entire solution, which consisted of a fully brand new PostgreSQL schema \& functions, Node.js API/RPC with web server backend, and custom web front-end.
\end {rSubsection}

\begin{rSubsection}{Tallan, Inc.}{November 2012 - February 2013}{Consultant}{Rocky Hill, Connecticut}
\item Performed deep and wide analysis of Prudential Financial, Inc.'s retirement solutions databases, including the 401 (k) and other defined contribution plans they manage.
\item Identified critical flaws in the design and content of the databases and recommended possible solutions/best practices.
\item Saved thousands of previously estimated man-hours by identifying inefficencies in current processes and subsequently designing and implementing custom analysis software to automate large parts of the analysis.
\item Contributed to a large store of data quality metrics that will be re-calculated and re-analyzed by the software as part of on going data quality measures.
\end {rSubsection}

\begin{rSubsection}{Software Marketing Associates, Inc.}{September 2007 - June 2012}{Senior Software Developer}{Rocky Hill, Connecticut}
\item Led small (5-7 people) team of developers to develop next generation of web-based fulfillment business software on top of the .NET platform.
\item Designed and implemented core frameworks and libraries used across the entire software solution including: data persistence, backend web server, frontend HTML/Javascript GUI, web services, Windows services, and others.
\item Designed and developed end-user installer that performed a non-trivial installation of many heterogenous components, including numerous legacy COM+ components, IIS hosted websites, MS SQL Server databases and various services.
\item Designed, developed and deployed software and processes to automate the entire code change lifecycle, from developer commit to the change running live on a customer's machine, both for multiple yearly releases and bi-weekly update deployments.
\item Developed and deployed numerous company-wide and department-wide tools for issue tracking, workflow automation and code generation.
\item Transitioned company from VSS source control and a manual copy-build-patch-deploy cycle to a continuous integration build cycle backed by Subversion and TeamCity.
\item Mentored and trained developers. Created and maintained a Wiki for the development team and authored other types of documentation.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Institute of Transportation Studies}{February 2006 - June 2007}{Developer}{Irvine, California}
\item Designed, implemented, tested and debugged integration software written
in C, C++, Visual C++, and C\# to allow .NET software to interoperate with
legacy C software.
\item Designed, implemented, tested and debugged software written in C\# with
extensive use of WinForms for visualizing data gathered from simulation
software.
\item Responsible for porting legacy plugins written in C to C\#.
\item Provided documentation and training to staff for software that was
developed.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of California, Irvine} \hfill {\em June 2007} \\ 
B.S. in Information \& Computer Science \\
With specializations in Computer Systems \& Networks and Distributed Systems \\
Overall GPA: 3.51/4.00

\end{rSection}

\end{document}
